---
title: "usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nsphsr)
```

The are the files of the NSPHS:

```
[richel@sens2021565-bianca NSPHS_data]$ ls
Methylation_All_Above_Dt_Bonferroni.RData  NSPHS.WGS.hg38.plink1.bed  NSPHS.WGS.hg38.plink1.log
NSPHS_age_sex_preg.csv                     NSPHS.WGS.hg38.plink1.bim  pea_1_2.rntransformed.AJ.RData
NSPHS_anthropometrics.csv                  NSPHS.WGS.hg38.plink1.fam  pea3.rntransformed.RData
```

These are the functions to re-create a simulated version of their data:

Filename                                   |Function
-------------------------------------------|--------------------------------------
`Methylation_All_Above_Dt_Bonferroni.RData`|None
`NSPHS_age_sex_preg.csv`                   |None, only one row
`NSPHS_anthropometrics.csv`                |None, only one row
`NSPHS.WGS.hg38.plink1.bed`                |`create_bed_table`
`NSPHS.WGS.hg38.plink1.bim`                |`create_bim_table`
`NSPHS.WGS.hg38.plink1.fam`                |`create_fam_table`
`NSPHS.WGS.hg38.plink1.log`                |`create_log_text`
`pea_1_2.rntransformed.AJ.RData`           |`create_pea_1`, `create_pea_2`
`pea3.rntransformed.RData`                 |`create_pea_3`


The package `nsphsr` contains three objects: `pea_1`, `pea_2` and `pea_3`.
All three are numeric matrices.
The column names are protein names.
The row names are (anonymized) individual names.
The values are normalized protein concentrations (i.e. mean is zero, 
67 percent of the values fall between -1.0 and +1.0), or are NA.
The total amount of NAs in each matrix matches the total amount of NAs
in the matrix of the orginal data

```{r}
knitr::kable(head(create_pea_1()))
```


```{r}
knitr::kable(head(create_pea_2()))
```


```{r}
knitr::kable(head(create_pea_3()))
```
